Unfolding the City: Exploring Urban Spatial Attractiveness with Individual Social Characteristics

### 2019-05-05 structure/structure.tex
new folder Structure

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Social Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\begin{abstract}
A city is shaped not only by its assembled infrastructures but also the people living inside it. People in a wide range of individual characteristics visit places with different weights and preferences, sculpturing the city into a space of diverse mobility patterns. Different from the well study of anonymous travel behaviors, the mobility patterns of characterized individuals, is less studied because of the challenges in collection and analysis of data with privacy. In this work, we take a step forward and perform an online census to collect individual profiles and movements from large-scale volunteers. Then we develop a visual analytic system to investigate the mobility patterns of groups by specifying characteristics. To facilitate the identification of characterized groups, individuals are embedded in t-SNE projection for an abstract overview as well as drawn as vivid graphics by a data-driven profile method for detail examination. A 2.5D spatial visualization is proposed to maintain a compact multivariable analysis by relaxing the z-axis to encode information, such as visiting frequency, demands, traveling distance, etc. Together with the cross-filter and flexible 2.5D interactions, the effectiveness and usability of the system are well demonstrated by a study made in Shenzhen.

\keywords{Visual analytics \and mobility pattern \and individual characteristics \and city }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\iffalse
What is it that makes some places, regions or nations appear more attractive than others to live in, visit or invest in? Does it depend on the particular characteristics or situation of the persons considering the attractiveness, in what phase in life the persons find themselves, or are there some common features, perhaps place characteristics that are viewed positively by all, independently of context?

\fi

\label{intro}
\wqc{change mobility pattern to spatial attractiveness}\\
The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities. Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}. Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

In the past decades, the power of visual analytics in exploring spatial-temporal data has been recognized and well developed. Transportation problems are answered by various movement data, such as traffic jams in taxi GPS trajectoires~\citep{wang2013visual}, interchanging flows in public transportation~\citep{zeng2013visualizing}, etc. The presence of social media applications fuels the spatial analysis with rich semantic texts, so researchers get the chances to explore the thematic meaning of the moving behavior, such as events~\citep{chen2017map} or topics~\citep{bosch2013scatterblogs2}. Those works essentially contribute in deepening the contextual understanding of moving activity. But they rarely combine the mobility with individuals' characteristics because which cannot be 100\% inferred from social media profiles. There is still a research gap in exploring the relationship between mobility pattern and characteristics.

In this work, we contextualize the analysis of mobility pattern in the backcloth of individual characteristics. Our motivation is to fuse the movement data with individuals' profiles in an attempt to ascertain the dynamics pattern of groups with different characteristics. To this, we need to get the characterized information of movers. The sensitivity issue in privacy data is one of the main challenges. The conventional offline census takes lots of effort and too much time to be out of date. With the wide use of the mobile device, it is possible to count information online. In this work, with a census survey released via social media application, we ran an online demographical collection campaign. Then we developed a visual analytics system to explore the mobility patterns centered around people. The system incorporates visualizations of individuals' characteristics, including t-SNE for an overview and data-driven profile visualization for the detailed check, as well as 2.5D spatial visualization to explore the mobility patterns. Finally, applying our method in Shenzhen, several cases are derived to demonstrate the powers of our method. There are two contributions of this work:

(1) investigate mobility patterns with characteristics, which is a natural step into research of social understanding of the city.

(2) develop a visual analytic system, whose effectiveness and usability is well demonstrated by a study made in Shenzhen.

@@

This work concerns the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\citep{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

\subsection{Movement data analysis}
 With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mine trajectory~\citep{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\citep{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\citep{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\citep{guo2011tripvista} and Zeng et al.~\citep{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\citep{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking. For multiple routes, Liu et al.~\citep{liu2011_routediversity} study the route diversity between locations and Lu et al.~\citep{Lu2017_multipleroute} explore the route choice behavior among multiple routes.

\subsection{Geo-tagged Social Media Data Analysis}
As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives. As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\citep{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\citep{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places. Krueger et al.~\citep{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\citep{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media. Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\citep{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\citep{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, the wrong inferring is inevitable. Longley et al.~\citep{Longley2015}~\citep{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

@@

% In the report (looking for some report), the penetration of mobile device is \m{XXX}, almost every XX people got a Mobile Phone in the urban.

@@

% Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc. The diverse purposes make it possible to characterize the flows across the city between different functional places.

@@

\section{Overview}

A discussion with experts in GIS. We summarize the analytic tasks identified from the interviews of domain experts. Then the workflow of the proposed visual analytics system.

\subsection{Goal}
\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\

Spatial attractiveness is an important concept to evaluate ... in commercial activity, tourism and urban research. We interview the expert in GIS. \lm{They identify \textit{Spatial Attractiveness}, and their correlation with individual social characteristics as the core research concern. Furthermore, they want to explore the space diversity according to its attractiveness to individuals.} \lmc{I think first we introduce spatial attractivenss, which is well defined by previous work. Then we explain the diversity of lands in attractivess (we need to find a better term), which we define. I think it is ok.}

\begin{itemize}
  \item \textit{Spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}

  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators. \wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}
\end{itemize}
With these questions, we summarize them into the tasks below, which need to be answered by our system.

\subsection{Tasks}
\lm{The exploration of core concepts above are resolved further with following tasks... to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}

%The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics\wqc{What kind of citizens tend to be attracted?}}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: What is the correlation between space and citizens? (Spatial Attractiveness)} to understand... group of citizens are attracted to different places, e.g., to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.

\item \textit{Task 3: What is the detailed properties of attractive differences?} ... How many citizens are extracted, the origins (Where do the attracted citizens come from?) What is the attractive differences over groups?

% City has different function areas. Some areas meet all the basic requirements of citizens' living activities, while some cannot. ...

% \item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ... \lmc{I don't think we can explain why...}
% \item \textit{Task 3: How many citizens are extracted?}: to express ... \lmc{I think it is just numbers, too weak to be a task}
% \item \textit{Task 4: Where do the attracted citizens come from?}: \lmc{also here}. City has different function areas. Some areas meet all the basic requirements of citizens' living activities, while some cannot. ... to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\end{itemize}

@@

% Classification method, flow clustering method, Semantic representation.

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure}
\fi

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/interface53}
 \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
 \label{fig:interfaceDraft}
\end{figure}

\section{Visual Design}

With those design considerations (introduced in Section~\ref{}), we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view. \lmc{Show a overview figure, to introduce the relationship between multiple views}

% overview of the data. Encode information but also allow users to set multiple criteria (\textit{C1}). Support users to slice the data by different domains.}
% Semantic understanding of social characteristics.

\subsection{Data-driven Profile Visualization}

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison. \lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparison over multiple individuals.}

\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common coordination configurations....}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/star53}
 \caption{\wq{star-like glyph for a group of citizens.}}
 \label{fig:interfaceDraft}
\end{figure}

\paragraph{Cartoon Glyph} ... Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variables by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C1}). Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

Figure~\ref{fig:design_profile} shows the legend for the user profile. The eight domains are encoded by visual symbols and organically organized in a human figure. There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones. For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness. For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning. For the boolean attribute like car, house, a symbol is designed to indicate its existence. With this consideration, the domains are designed as follows:

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
 \label{fig:design_profile}
\end{figure}

% For numeric attributes.

% By different composition, stimulus pattern which has the abstract demographic measurement of individuals.

@@

\subsection{T-SNE Projection}

@@

\subsection{HAVE NO TILE FOR THIS}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view. \wqc{lack of a FIGURE}

@@

\lmc{Add a section to introduce the domain experts' feedback}

\lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}

\section{Case study}

@@

\wq{\subsection{Case 1: find diversity of citizens based on social characteristics}}
\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces in view3 and view4. text no changes yet.}

This work is inspired and motivated by the implication in science fiction~\textit{Folding Beijing}, which is that people are categorized into three classes and behave in the parallel spatial-temporal patterns. The first cast explores whether the folding city exists in reality or not.

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_1}
 \caption{Four Groups Divided by Income and Education Characteristics}
 \label{case11}
\end{figure}

Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not.\\
\wq{EDIT paragraph below. not just give number, use view1 and view2 to filter the target groups.}\\
As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants. In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}. The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income. In the third quadrant, they are the \textit{underclass} who has both low income and education level. The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.

Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group. In each group, other characteristics surprisingly demonstrate the high correlation to income and education. For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car. On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car. Most of \textit{New rich} has a house and work in the service industry.

Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups. As Figure~\ref{case1draft} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost. A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown. The \textit{underclass} distribute more dispersively all over the whole city. Compared to the rich, they prefer the outer space because of the lower living cost. Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.

\wq{The glyphs on the map means the travel distance, travel radius..., which is an important in mobility research. Describe the difference.}\\
\wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator.}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c1-s3-53}
 \caption{Home Distributions of the Four Groups}
 \label{case1draft}
\end{figure}

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home Distributions of the Four Groups}
 \label{case12}
\end{figure}

To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends. Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories. Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''. Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}. It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups. To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups. Figure~\ref{case13}(b) shows three slices. It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}. Working percentage is very small in-group \textit{new rich}. They live a more diverse lifestyle because they do many other things (the pink ones) except working.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_3}
 \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
 \label{case13}
\end{figure}
\fi

\subsection{Case 2: Spatial Attractiveness}
\wqc{aim: select one purpose to show how many and where and how long.}
\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}

\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}

\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. }
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c2-s2-53}
 \caption{For purpose of shopping: (a) the rich; (b) the poor.}
 \label{case3draft}
\end{figure}

\wq{After clicking a target grid, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$. Compare two grid which have similar quantity, the distributions differ.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c2-click-s2-53}
 \caption{For purpose of shopping: (a) spatial attractiveness of the poor; (b) Grid1; (c) Grid2.}
 \label{case3draft}
\end{figure}

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case2}
\end{figure}

Home-work distance is an essential metric in economics, geography, and sociology. It refers to the distance between house and workplace. It is influenced by many factors like transportation, housing, land use, etc. Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not. In this case, we demonstrate our system's help in home-work distance understanding.

Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K. In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far. As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown. Only those with less than 100K salary work outside the center, such as the space in the green circle. When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.

We explore the home-work distance of groups with and without a house.
Figure~\ref{case2}(b) shows the close-up views. It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house. Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
\fi

\subsection{Case 3: Diversity of spatial attractiveness of indicators}
\wqc{aim: with mixed purposes, show attractiveness quantity and entropy. View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

\wq{Due to the various functions of the areas, for different space, the attractiveness indicators differs. Therefore, in this case, we demonstrate the use of the system for exploring diversity of spatial attractiveness indicators. }

\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$. \wqc{(if we decide to give a computing equation to define it.)}\lmc{I think we can define a equation to compute it.} in view 4, ranking of each grid based on the quantity of each purpose.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c3-53}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case2draft}
\end{figure}

In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement. Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}. The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose. There are 10 different kinds of traveling purposes. For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color. As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height. Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs. The relative percentage of irregular activity differs for the four groups. For Workman, about 80 percent of movements are the regular purpose, either go to work or go back home. For students, the percentage becomes to be about 50 percentage. Compared to them, officer and businessman have more flexible and diversified lifestyle.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case3}
\end{figure}

Next, we concentrated on one purpose to see whether it is related to jobs. Here we use ``dinner or entertainment" as the example. As Fig \ref{case32} shows, the height of TAZ bars represents the visiting amount of trips for dinner or entertainment. Color stands for moving distance to reach this TAZ. As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area. Students tend to concentrate on Nanshan district, probably near schools. For the businessmen, they go lots of places for dinner or entertainment. The biggest difference with other groups is that they would travel a long distance to go somewhere far from downtown areas.

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}
\fi

\section{Conclusion}
\label{sec:conclusion}

This work demonstrates a throughout research flow from data collection, basic analysis to deep visual analysis of mobility patterns with individual characteristics. Considering the irresistible trend in mixing social data and spatial data to solve the urban problem, this work takes one step forward in exploring the relationship between movement and individuals' characteristics, which is rarely touched by previous geo-tagged social media visual analytics. The design of the visual analytic system is driven by three tasks about individuals and mobility patterns. Tapping into our daily experiences, the data-driven profile visualization provides an organic and intuitive representation of individuals. Its effectiveness in identifying similar or abnormal individuals from the mass has been demonstrated. The design of 2.5D spatial visualization continues the exploration of the typical research problem how to visualize spatial information and abstract information together. Although it is not a one-step solution, 2.5D visualization with the detail slicing is able to provide an occlusion-free analysis with spatial context preserved.

Our current research focuses on fundamental facets of the mobility patterns and doesn't draw a strong conclusion on the correlation between mobility pattern and individual characteristics. In next step, more delicate algorithms will be involved to extract high-level mobility patterns, such as the frequent visiting sequence of an individual group, etc. On the other hand, the data we used in this work shows its potential in representing the population. As the next step, research effort can be put into a more serious verification of how small sampled data can represent a large population.

>>>>

\title{Unfolding the City: Exploring Urban Spatial Attractiveness with Individual Social Characteristics}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\begin{abstract}

\keywords{Visual analytics \and spatial attractiveness \and individual characteristics \and city }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\iffalse
What is it that makes some places, regions or nations appear more attractive than others to live in, visit or invest in? Does it depend on the particular characteristics or situation of the persons considering the attractiveness, in what phase in life the persons find themselves, or are there some common features, perhaps place characteristics that are viewed positively by all, independently of context?
\fi

\paragraph{bgm}

\paragraph{past, trajectory, not social characteristics}

\paragraph{in this paper}

\paragraph{novelty}

@@

@@

@@

@@

\section{Overview}
By communicating with domain expert, we summarize the analytic tasks identified from the interviews of domain experts. Aimed at these tasks, we derive design considerations and introduce the workflow of the proposed visual analytics system.

\subsection{Background}

For understanding how to express spatial attractiveness, we have several interviewers with an expert in GIS who works on human mobility and urban informatics. The experts pointed out that the study of social-spatial interactions has become more important with big and open data evolved in. Instead of evaluated by static indicators, such as the characteristics of the spatial facilities, spatial attractiveness can be evaluated dynamically with human movement data. People have their own preferences when they go out for a specific purpose. It reflects the attractiveness of the place they selected. When the research scale is expanded into city-scale, whether spatial attractiveness is similar of the citizens with similar social characteristics. However, for GIS researchers, there is no efficient and effective methods which help to explore spatial attractiveness, citizens with multiple social characteristics, and their relationships. After several rounds of interviews with experts, we summarize the main analysis criteria below:

\begin{itemize}
\item \textit{Multiple social characteristics}

\item \textit{Spatial attractiveness} In urban planning and GIS, the definitions of spatial attractiveness is based on gravity model\wqc{add refer}. It means the more distant the less attractiveness. Hence, both the quantity of people attracted and movement distances are two crucial concepts to be explored.

\item \textit{Attractiveness diversity} In urban planning, functional area is an important concept. When the area has more functions, for people here, their living requirements are more easily met, the attractiveness diversity of the area is higher.  ......

\end{itemize}

\subsection{Tasks}
The exploration of core concepts above are resolved further with following tasks... to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics\wqc{What kind of citizens tend to be attracted?}}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: What is the correlation between space and citizens? (Spatial Attractiveness)} to understand... group of citizens are attracted to different places, e.g., to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\item \textit{Task 3: What is the detailed properties of attractive differences?} ... How many citizens are extracted, the origins (Where do the attracted citizens come from?) What is the attractive differences over groups?
\end{itemize}

@@

\section{Visual Design}
\begin{figure}[htb!]
 \centering 
 \includegraphics[width=\linewidth]{pictures/interface53}
 \caption{\wqc{to be edit. System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
 \label{fig:interfaceDraft}
\end{figure}

With those design considerations described before, we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven social profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, spatial attractiveness is visualized and explored in a map view with the \wqc{no name} glyph we designed.

\subsection{Social Profile Visualization}
To express the multiple dimensional social characteristics, we use three scales: bar glyph for all citizens, octagon glyph for a group of persons, and cartoon glyph for one person.

\paragraph{Bar Glyph}
As shown in Figure~{\ref{fig:interfaceDraft}}(a), bar glyphs are used to encode quantitative relationships. For each characteristic, we compute the quantity and the percentage of each type, and encode it in the length of the bar. Interaction is also bound. When clicking a bar, filtering will be done, and the filtering result will be used in grouping phrase.

\paragraph{Octagon Glyph}
Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison.

\paragraph{Cartoon Glyph}
Among glyph design, Chernoff Face (Chernoff, 1973) represents data variables by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (C1). Those visual profiles are intended for intuitive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

\begin{figure}[htb!]
 \centering 
 \includegraphics[width=0.6\columnwidth]{pictures/cartoonglyph}
 \caption{***********************}
 \label{fig:cartoon}
\end{figure}

Figure~\ref{fig:cartoon} shows the legend for the user profile. The eight domains are encoded by vi- sual symbols and organically organized in a human figure. There are basically three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones. For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness. For the categorical attributes such as job, visual symbols are designed separately for better semantic meaning. For the boolean at- tribute like car, house, a symbol is designed to indicate its existence. With this consideration, the domains are designed as follows:

@@

\subsection{T-SNE Projection of Individuals}

@@

\subsection{Location-based multidimensional grid visualization}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embed in the map view.

@@

\lmc{Add a section to introduce the domain experts' feedback}
\lm{We interview XX domain experts from the GIS field. XX of them are with ... The procedure went as following. We first introduce them the system an...}

\section{Case studies}

@@

\subsection{Case 1: Group by similar social characteristics}
\paragraph{Use bar and tsne to find four groups. figure to show groups.}
\paragraph{Their home locations and basis travel features.}

\subsection{Case 2: Spatial Attractiveness}
\paragraph{Select two groups, and target purpose. figure to compare spatial attractiveness.}
\paragraph{click a grid, show OD. figure}

\subsection{Case 3: Diversity of spatial attractiveness}
\paragraph{Select group, figure to show diversity.}
\paragraph{ranking, figure}
\paragraph{two groups to compare, figure}

\section{Discussion and Conclusion}
